Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-08 paper.tex
retoques nas conclusoes

\section{Conclusions}\label{sec:conc}
The temporal stability reported in this article is very counterintuitive.
These characteristics were expected from current scientific knowledge,
such as the fat tail structure and the preponderance of centrality measures,
but the very small standard deviations of principal components formation
(see Sections~\ref{sec:pca} and~\ref{prevalence}),
the presence of the Erd\"os sectors even in networks with
few participants (see Sections~\ref{sectioning} and~\ref{subsec:pih}),
and the recurrent activity patterns along different timescales (see Sections~\ref{sec:mtime} and~\ref{constDisc}),
goes a step further in characterizing scale-free networks in the context
of the interaction of human individuals.
Maybe secondary, but nonetheless important, the importance of symmetry-related metrics,
which surpassed that of clustering coefficient,
with respect to dispersion of the system in the topological space,
might add to current understanding of key-differences between digraphs and
undirected graphs in complex networks.
Noteworthy is the also very stable fraction participants in each Erd\"os sector
when the network reaches more than 200 participants (more that 1000 messages).
Benchmarks were derived from email list networks
and the supplied analysis of
networks from Facebook,
Twitter and Participabr might ease hypothesizing
about the generality of these characteristics.
Selected tables and figures sum dozens of pages
and are gathered in
the Supporting Information document.

Further work should expand the analysis to include
more types of networks and more metrics.
The data and software needed to reach these results
might also receive dedicated and in-depth
documentation as they enable a greater level of transparency
and work share,
which is adequate to both benchmarking
and the study of systems constituted
by human individuals (see Section~\ref{sec:data}).
The derived typology of hub, intermediary and peripheral participants
was used for semantic web and participatory democracy efforts,
and might be enhanced to yield scientific knowledge~\cite{opa}.
Also, we should pursue the publication of the visualization and sonification
processes used for this research~\cite{versinus,animacoes} and
of the extreme linguistic differences found in each of the Erd\"os sectors~\cite{rcText}.

>>>>

\section{Conclusions}\label{sec:conc}
The temporal stability reported in this article is very counterintuitive.
These characteristics were expected from current scientific knowledge,
such as the fat tail structure and the preponderance of centrality measures,
but the very small standard deviations of principal components formation
(see Sections~\ref{sec:pca} and~\ref{prevalence}),
the presence of the Erd\"os sectors even in networks with
few participants (see Sections~\ref{sectioning} and~\ref{subsec:pih}),
and the recurrent activity patterns along different timescales (see Sections~\ref{sec:mtime} and~\ref{constDisc}),
goes a step further in characterizing scale-free networks in the context
of the interaction of human individuals.
Furthermore, the importance of symmetry-related metrics,
which surpassed that of clustering coefficient,
with respect to dispersion of the system in the topological space,
might add to current understanding of key-differences between digraphs and
undirected graphs in complex networks.
Noteworthy is the also very stable fraction participants in each Erd\"os sector
when the network reaches more than 200 participants.
Benchmarks were derived from email list networks
and the supplied analysis of
networks from Facebook,
Twitter and Participabr might ease hypothesizing
about the generality of these characteristics.
Selected tables and figures sum dozens of pages
and are gathered in
the Supporting Information document.

Further work should expand the analysis to include
more types of networks and more metrics.
The data and software needed to reach these results
might also receive dedicated and in-depth
documentation as they enable a greater level of transparency
and work share,
which is adequate to both benchmarking
and the study of systems constituted
by human individuals (see Section~\ref{sec:data}).
The derived typology of hub, intermediary and peripheral participants
was used for semantic web and participatory democracy efforts,
and these developments might be enhanced to yield scientific knowledge~\cite{opa}.
Also, we should pursue the publication of the visualization and sonification
processes used for this research~\cite{versinus,animacoes} and
of the extreme linguistic differences found in each of the Erd\"os sectors~\cite{rcText}.
